\Large Analyzing the Supreme Court Citation Network

### 2017-12-01 Tex/paper.tex
added introduction

 Coming...

>>>>

Majority opinions written by the US Supreme Court exercise their authority and influence, in part, through their roles as precedents in future Supreme Court decisions and opinions [CITES]. Research on the nature of {\em Stare Decisis}---the Court's reliance on precedent---has been mixed, with some finding that past opinions influence and constrain future opinions [CITES], and others finding that, while referenced in opinions, past cases do not effect the Court's current behavior [CITES].
